---
title: "R Notebook"
output: html_notebook
---


Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*. 
Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

Preparation
```{r}
# Load the packages
library(ggplot2)
library(readr)
# import pandas in python

# read the data

# simulating data

 # participants
potentialBackground = c()

# explore 3 subgroups
nSubs = 3
nSubGourp1 = 60

# condition
nConds = 2
condLabels = c("pre, mid, post")

# nTrialPerCond = 

# outcome measure
# reaction time/likert responses...

# think through df
# row - participant
# column - condition, DVs, demo

df <- data.frame(participant=rep(0,sample_sizeRequired),
                 Condition=rep("NA", sample_sizeRequired),
                 ReactionT=rep("NA", sample_sizeRequired),
                 Accuracy=rep(0,sample_sizeRequired),
                 likert=rep(0,sample_sizeRequired),
                 stringsAsFactors=TRUE)

df$participant = seq(1,sample_sizeRequired, each=condPerParticipant)

df$condition <- sample(condLabels, sample_sizeRequired, replace = TRUE)

# background


# random distribution
df$ReactionT = rnorm(sample_sizeRequired, mean=700, sd=200)

df$ReactionT[df$condition == "AI"] = df$ReactionT +500



# 
df$likert <- sample(c(1:7), sample_sizeRequired, replace=TRUE)

```



Explore
```{r}
# print
head(df)

# formatting / cleaning

# conversion of data types. 
summary()
as.numeric() # change to number

# dealing with missing data

# remove unnecessary data

# remove according to exclusion criteria

```


Exploration
```{r}
# summary / descriptive stats

# check variable distribution

# correlation

# scatterplot between 2 variable

```

Demographic 
```{r}
# mention in the paper

# mean and sd of age

# experience
```

Inferential Stats
```{r}
anova()
t.test()


# DV - IV

```

Visualization
```{r}
# Bar plot
# error + sem

# point estimate

# linear
```

Exploratory
```{r}
# 
```






Load the file
```{r}
library(ggplot2)

getwd()
setwd("D:/Google 下载")
df <- read.csv("mydata (5).csv")
```

Rearrange the data frame
```{r}
df_single <- df[1, c("somatic_score", "worry_score", "concentration_score")]

# Convert to long format for plotting
df_long <- data.frame(
  Score_Type = c("Somatic", "Worry", "Concentration"),
  Score = as.numeric(df_single))
```


Individual score visualization
```{r}
ggplot(df_long, aes(x = Score_Type, y = Score, fill = Score_Type)) +
  geom_bar(stat = "identity") +
  labs(title = "Comparison of Three Scores",
       x = "Score Type",
       y = "Score") +
  theme_minimal()
```

